\textsf{Are large language models superhuman chemists?}

### 2024-03-20 src/tex/appendix.tex
update manuscript
update text
move details to appendix

\subsection{Human baseline}

\begin{figure}
    \centering
    \includegraphics{figures/human_timing.pdf}
    \script{analyze_human_data.py}
    \label{fig:human_timing}
    \caption{\textbf{Time taken by human scorers to answer questions vs.\ correctness of their answers.} From the plot it is clear that there is no clear dependence of the correctness of the answers on the time taken by the human scorers to answer the questions.}
\end{figure}

@@

\begin{figure} 
    \centering
    \includegraphics{figures/confidence_score_distributions.pdf}
    \caption{\textbf{Distribution of confidence scores reported by \glspl{llm}.} \Glspl{llm} show different distributions of confidence scores. The confidence scores are reported on an ordinal scale from 1 to 5, with 1 indicating low confidence and 5 indicating high confidence. The barplots show how many questions were answered with each confidence score.}
    \label{fig:confidence_score_distributions}
    \script{plot_confidence_score_distributions.py}
\end{figure}

\printnoidxglossary[type=\acronymtype]  % https://github.com/tectonic-typesetting/tectonic/issues/704

>>>>

\subsection{Human baseline}
\paragraph{App} To facilitate the collection of responses, we developed a responsive web application in Typescript using the Next.js\autocite{nextjs} app router framework.
This application handles serving the user interface as well as exposes various \gls{rest} \glspl{api} for relevant operations.
We utilize a MySQL\autocite{mysql} database and Prisma \gls{orm}\autocite{prisma} for efficient database management.
The web application is styled with Tailwind CSS\autocite{tailwindcss} using the shadcn/ui component library and uses NextAuth\autocite{nextauth} for easy and secure user authentication and postMark for sending Emails.
The application is hosted on the Vercel web hosting platform.

\begin{figure}[htb]
    \centering
    \includegraphics{figures/human_timing.pdf}
    \script{analyze_human_data.py}
    \label{fig:human_timing}
    \caption{\textbf{Time taken by human scorers to answer questions vs.\ correctness of their answers.} From the plot it is clear that there is no clear dependence of the correctness of the answers on the time taken by the human scorers to answer the questions.}
\end{figure}

@@

\begin{figure}[htb] 
    \centering
    \includegraphics{figures/confidence_score_distributions.pdf}
    \caption{\textbf{Distribution of confidence scores reported by \glspl{llm}.} \Glspl{llm} show different distributions of confidence scores. The confidence scores are reported on an ordinal scale from 1 to 5, with 1 indicating low confidence and 5 indicating high confidence. The barplots show how many questions were answered with each confidence score.}
    \label{fig:confidence_score_distributions}
    \script{plot_confidence_score_distributions.py}
\end{figure}

\clearpage

\printnoidxglossary[type=\acronymtype, nonumberlist]  % https://github.com/tectonic-typesetting/tectonic/issues/704

### 2024-03-20 src/tex/ms.tex
move details to appendix

\paragraph{Models}
\subparagraph{Completion models}
We used \texttt{Galactica-120b}\autocite{taylor2022galactica} with the default settings.

\subparagraph{Instruction-tuned models} In addition, we used \texttt{Claude 2}, \texttt{Claude3 (Opus)},\autocite{anthropicClaudeModelFamily2024} \texttt{GPT-4},\autocite{openai2024gpt4} \texttt{GPT-3.5-turbo},\autocite{brown2020language}
\texttt{Gemini Pro},\autocite{gemini}
\texttt{Mixtral-8x7b}\autocite{jiang2024mixtral}
\texttt{Llama2-70b},\autocite{touvron2023llama}
\texttt{pplx-7b-chat}

@@

\subsection{Confidence estimate}
To estimate the models' confidence we prompted them with the question (and answer options for \gls{mcq}) and the task to rate their confidence to produce the right answer on a scale from 1 to 5.

@@

\paragraph{App} To facilitate the collection of responses, we developed a responsive web application in Typescript using the Next.js\autocite{nextjs} app router framework.
This application handles serving the user interface as well as exposes various \gls{rest} \glspl{api} for relevant operations.
We utilize a MySQL\autocite{mysql} database and Prisma \gls{orm}\autocite{prisma} for efficient database management.
The web application is styled with Tailwind CSS\autocite{tailwindcss} using the shadcn/ui component library and uses NextAuth\autocite{nextauth} for easy and secure user authentication and postMark for sending Emails.
The application is hosted on the Vercel web hosting platform.

>>>>

\paragraph{Models}
\subparagraph{Completion models}
We used Galactica (120b)\autocite{taylor2022galactica} with the default settings.

\subparagraph{Instruction-tuned models} In addition, we used Claude 2, Claude3 (Opus),\autocite{anthropicClaudeModelFamily2024} GPT-4,\autocite{openai2024gpt4} GPT-3.5-turbo,\autocite{brown2020language} Gemini Pro,\autocite{gemini} Mixtral-8x7b\autocite{jiang2024mixtral} Llama2 (70b),\autocite{touvron2023llama} as well as the 7B chat model from Perplexity.AI.

@@

\subsection{Confidence estimate}
To estimate the models' confidence we prompted them with the question (and answer options for \gls{mcq}) and the task to rate their confidence to produce the right answer on a scale from 1 to 5. 
We decided to use verbalized confidence estimates\autocite{xiong2023llms} since we found those closer to current practical use cases compared to other prompting strategies, which might be more suitable when implemented in systems.

@@
